---
title: "Exploratory Analysis"
author: "Sam Cooke, Jianhong Dong, Eric Fan, Jason Hyun Jung"
date: "`r Sys.Date()`"
---
# Intro
  Our group decided to analyze data from the stock market, more specifically, the biggest players in the tech sector. We first became interested in this topic after seeing all of the excitement in the stock market with Gamestop earlier this year. The dataset we selected looks at a few important values from 100 important companies. There are 9 variables in the dataframe, starting with the ticker symbol for each stock, and the name of the company. There is also price of the stock, daily change in both dollars and percent, daily volume of the stock traded, average volume of the stock, market capitalization in billions, and P/E ratio. Market cap is a valuation of how much a company is worth, calculated by number of outstanding shares multiplied by share price. P/E ratio is the ratio of share price to the company's most recent earnings per share. It is a good way to determine if a company is over/under valued. We hope that we can analyze this data and become better acquianted with the stock market, as well as how these variables interact with eachother. 


# Summary Information

```{r, echo = FALSE, message =FALSE}
source('summary.R')
```

With our summary information, we decided to pull a few values that we thought could be important for comparison. Eventually we want to look at individual companies, so it is important to see what the average company's market capitalization is, as well as the median market cap. It's very clear that the average market cap is much larger than the median, at 94.6B vs 32.1B. This means that the huge outlier companies like apple and Microsoft are so big that they bring up the average, and that the data is left skewed. The number of observations is 100, which is important because it allows us to see the scale of the companies that we are working with. We also calculated the max market cap which was 1.936 Trillion dollars, and we felt that it was important because it puts into perspective the respective market caps of the other companies. We decided to put so much value on market cap because it is the actual valuation of a company, as the share price is only as valuable as the amount of shares available. We also calculated the average price of a share of a company, to see how much capital one would need to get started investing in them. Finally, we calcualted average volume, because it is an extremely important factor in the liquidity of an individual company, so it is a good value to compare to.

# Table


```{r, echo = FALSE, message =FALSE}
source('AggregateChart.R')
```

By grouping companies that gained more than one percent, less than one percent, lost more than one percent, and less than one percent, we can see the number of companies that gained or lost stocks with the one percent margin.

We found that most companies gained more than 1% (44 companies), 27 companies gained less than 1%, while 16 companies lost less than 1% of their stocks, and 13 companies lost more than 1% of their stocks.

# Charts



### Chart 1

```{r, echo = FALSE, message =FALSE}
source('FirstChart.R')
```

This chart was made to display that when the price is high for a stock, they would have more change as for stocks with lower price have the chance to be volatile. 



### Chart 2

```{r, echo = FALSE, message =FALSE}
source('SecondChart.R')
```

This chart was made to rank the change in the stock price of the companies, so that we can see which companies did better on that day compared to the other ones.
This chart shows all the price changes of the top 100 tech companies and it’s ranked from the highest to lowest. From this chart we will be able to see what companies have their prices increased the most and what have their prices decreased the most. From the chart I noticed that more companies have  positive price changes than companies have negative price changes. And the most price increased is around 15 which is more than the most price decreased(around 7). So in general more companies tend to have positive price changes and the changes are usually larger than the negative changes




### Chart 3

```{r, echo = FALSE, message =FALSE}
source('ThirdChart.R')
```

This chart looks at the relationship between average volume and the price per share of
a stock. I think that this might be an interesting relationship because companies with a
higher market cap generally have a higher price per share, and there large market cap companies
are traded usually with more volume because of how important and recognizable they are.
Another factor that goes into this relationship is that some retail investors can't afford
to buy some highly priced stocks, so that might drive the volume down. Additionally,
cheaper stocks are bought in larger quantities, which would drive the volume down for higher priced stocks. Either way, I think it might be interesting to see.